%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{xspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\def\plusplus{\texttt{++}\xspace}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItemList}[1]{
{\justifying
  \item{#1 \vspace{-6pt}}
\par}
}

\newcommand{\resumeItem}[2]{
{\justifying
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
\par}
}
 
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingList}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
      \textit{#5} &  \\
    \end{tabular*}\vspace{-5pt}
}




\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://zoranzhao.github.io/}{\Large Zhuoran Zhao}} & Email : \href{mailto:zhuoran@utexas.edu}{zhuoran@utexas.edu}\\
  \href{https://zoranzhao.github.io}{Personal Website: https://zoranzhao.github.io} & Mobile : +1-512-751-1819  \\
  \href{https://github.com/zoranzhao}{GitHub: https://github.com/zoranzhao}  &\\
  \href{https://www.linkedin.com/in/zoranzhao}{LinkedIn: https://www.linkedin.com/in/zoranzhao} &  \\
\end{tabular*}

\section{Summary}
{\justifying
My research interests include efficient runtime/middleware for distributed deep learning, system-level performance modeling and software/hardware co-design.
\vspace{-5pt}
\par}
%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
      \resumeItemList{{\bf Programming languages}: C/C\plusplus, Python}
      \resumeItemList{{\bf Tools and frameworks}: LLVM, Caffe2, PyTorch, Darknet, OMNeT++, lwIP.}
      \resumeItemList{Project experiences with operating system kernel programming, multi-threaded programming (POSIX pthreads) and network programming (Socket Programming in C).}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingList
      {Ph.D. in Electrical and Computer Engineering;}{Dec. 2014 -- May 2019}
      {University of Texas at Austin;}{Austin, Texas}
      {Advisor: Prof. Andreas Gerstlauer}
    \resumeSubheading
      {M.S. in Electrical and Computer Engineering;}{Aug. 2012 -- Dec. 2014}
      {University of Texas at Austin; GPA: 3.93/4.00}{Austin, Texas}
    \resumeSubheadingList
      {B.S. in Electrical Engineering;}{Sep. 2008 -- Jun. 2012}
      {Zhejiang University; GPA: 3.95/4.00}{Zhejiang, China}
      {Honored Minor: Advanced Honor Class of Engineering Education (ACEE)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Facebook}{Menlo Park, CA}
      {Research Scientist}{Oct. 2019 - Present}
      \resumeItemListStart
        \resumeItemList{Ads Machine Learning (ML) Ranking Infrastructure}
        \resumeItemList{Distributed AI Infrastructure}
        \resumeItemList{Large Scale Machine Learning (ML) Recommendation System}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Austin}{Austin, Texas}
      {Graduate Research Assistant/Teaching Assistant}{Aug. 2012 - May 2019}
      \resumeItemListStart
        \resumeItem{DeepThings}
          {Research project focusing on a portable and lightweight runtime framework for locally distributed CNN/DNN inference in resource-constrained IoT edge clusters, developed in C~\ref{DeepThings}.}
        \resumeItem{Network-of-Systems Simulator (NoSSim)}
          {Research project focusing on a source-level network/system co-simulation framework for distributed embedded/mobile computing cluster prototyping, developed in C\plusplus with LLVM, OMNeT\plusplus and SystemC framework~\ref{NoSSim}.}
        \resumeItemList{Teaching Assistant:  EE382N Embedded System Design and Modeling (Fall 2015), EE319K Introduction to Embedded Systems (Fall 2012)}
        %\resumeItem{HCSim}
        %  {A fast full-system simulation platform with abstract models of real-time operating systems (RTOS) and high-level multi-core processor models, developed in C\plusplus with SystemC framework~\ref{NoSSim}.}
        %\resumeItem{RBA}
        %  {A compile-time profiling and instrumentation tool for source-level system performance evaluation, developed in C\plusplus and python with GCC and LLVM framework~\ref{PERPT}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheadingList
      {FutureWei Technologies}{Plano, Texas}
      {Research Intern}{May 2014 - Aug. 2014}
      {Manager: Weizhong Chen}
      \resumeItemListStart
        \resumeItemList{Architectural Description Language (ADL) framework prototype for digital signal processors (DSP), developed in C\plusplus and Python.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheadingList
      {NXP Semiconductors}{Austin, Texas}
      {Research Intern}{May 2013 - Aug. 2013}
      {Manager: Mark Bader}
      \resumeItemListStart
        \resumeItemList{Automatic microprocessor performance calibration framework between RTL and cycle-accurate simulator, developed in C\plusplus with ADL/uADL framework.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheadingList
      {University of California, Los Angeles}{Los Angeles, California}
      {Summer Exchange Program}{Jul. 2011 - Sep. 2011}
      {Advisor: Prof. Vwani P. Roychowdhury}
      \resumeItemListStart
        \resumeItemList{Interactive complex network visualization in mobile applications and browsers, developed in JavaScript, Java and Python with AJAX technique and Django framework.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\newcommand{\reference}[2]{\justifying\textbf{``#1,''}{\it #2}\par}



%-----------PUBLICATIONS-----------------
\section{Selected Publications}
\begin{enumerate}[label={[\arabic*]}, leftmargin=*]

  \item \label{DeepThings} {{Zhuoran Zhao}, K. Mirzazad and A. Gerstlauer, \reference{DeepThings: Distributed Adaptive Deep Learning Inference on Resource-Constrained IoT Edge Clusters} 
    {CODES+ISSS, special issue of IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2018.} \vspace{-3pt}}
  \item \label{NoSSim} {{Zhuoran Zhao}, V. Tsoutsouras, D. Soudris, A. Gerstlauer, \reference{Network/System Co-Simulation for Design Space Exploration of IoT Applications} 
    {Proceedings of the International Conference on Embedded Computer Systems: Architectures, Modeling and Simulation (SAMOS), 2017.} \vspace{-3pt}}
  \item \label{PERPT} {{Zhuoran Zhao}, A. Gerstlauer and Lizy K. John, \reference{Source-Level Performance, Energy, Reliability, Power and Thermal (PERPT) Simulation} 
    {IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2017.} \vspace{-3pt}}
  \item \label{Web} {Zhuoran Zhao, D. Lee and A. Gerstlauer, \reference{Host-Compiled Reliability Modeling for Fast Estimation of Architectural Vulnerabilities} 
    {In Silicon Errors in Logic, System Effects Workshop (SELSE), 2015} \vspace{-3pt}}
  \item \label{RBA} {S. Chakravarty, { Zhuoran Zhao}, A. Gerstlauer, \reference{Automated, Retargetable Back-Annotation for Host-Compiled Performance and Power Modeling} 
    {Proceedings of the IEEE/ACM/IFIP International Conference on Hardware/Software Codesign and System Synthesis (CODES+ISSS), 2013.} \vspace{-3pt}}
  \item \label{Web} {L. Guckert, M. O'Connor, S. K. Ravindranath, { Zhuoran Zhao} and V. J. Reddi, \reference{A Case for Persistent Caching of Compiled JavaScript Code in Mobile Web Browsers} 
    {In Workshop On Architectural And Microarchitectural Support For Binary Translation (AMAS-BT), 2013} \vspace{-3pt}}



\end{enumerate}


%-----------Relevant Graduate Coursework-----------------
\section{Relevant Graduate Coursework}
  \resumeSubHeadingListStart
	\resumeItemList{EE382V Dynamic Compilation}
	\resumeItemList{EE382V Advanced Programming Tools}
	\resumeItemList{EE380L Engineering Programming Languages}
	\resumeItemList{EE382C Multicore Computing}
	\resumeItemList{EE382N Computer Architecture}
	\resumeItemList{EE382N Embedded System Design and Modeling}
	\resumeItemList{EE382M System-on-a-Chip Design}
  \resumeSubHeadingListEnd


%-----------Relevant Graduate Coursework-----------------
\section{Professional Service}
  \resumeSubHeadingListStart
	\resumeItemList{\bf Reviewer:\vspace{-5pt}}
	\resumeItemListStart
		\item IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2017 \vspace{-3pt}
		\item Design, Automation and Test in Europe (DATE) Conference, 2018 \vspace{-3pt}
		\item IEEE/ACM/IFIP International Conference on Hardware/Software Codesign and System Synthesis (CODES+ISSS), 2018 \vspace{-3pt}
	\resumeItemListEnd

	\resumeItemList{\bf Teaching:\vspace{-5pt}}
	\resumeItemListStart
		\item Teaching Assistant:  EE382N Embedded System Design and Modeling, 2016 \vspace{-3pt}
		\item Teaching Assistant: EE319K Introduction to Embedded System, 2012 \vspace{-3pt}
	\resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Honors and Awards}
  \resumeSubHeadingListStart
    \resumeItemList{Best in Session Award for the presentation ``Automated, Retargetable Back-Annotation for Host-Compiled Power
and Performance Modeling,'' in Semiconductor Research Corporation (SRC) TECHCON, Sep 11, 2013}
    \resumeItemList{National Scholarship in China (2\%), 2009, 2010}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

